%==================================acknowledgement.tex=============================

    \chapter*{\centering ACKNOWLEDGEMENT}

\subfile{design_cover}
\addcontentsline{toc}{chapter}{Acknowledgement}%

%\newenvironment{acknowledgement}
We take this opportunity to express our gratitude to the people who have been instrumental in the successful completion of this project. We would like to express our profound gratitude to the Management and Dr. N.V.R Naidu Principal, M.S.R.I.T, Bengaluru for providing us with the opportunity to explore our potential.

We extend our heartfelt gratitude to our beloved Dr. Siddesh G M, HOD, Department of
Computer Science and Engineering (AI&ML), for constant support and guidance.

We whole heartedly thank our mini project guide Dr. A N Ramya Shree, for providing us with the confidence and strength to overcome every obstacle at each step of the project and inspiring us to the best of our potential. We also thank Dr. A N Ramya Shree, Mini Project Coordinator for her constant guidance, direction and insight during the project.

This work would not have been possible without the guidance and help of several individuals who in one way or another contributed their valuable assistance in preparation and completion of this study.

Finally, we would like to express sincere gratitude to all the teaching and non-teaching faculty of Computer Science and Engineering (AI&ML) Department, our beloved parents, seniors and my dear friends for their constant support during the course of work.
\\


\begin{flushright}
Saikiran Ponde (1MS23CI106)\\
Shreenath Shenoy (1MS23CI112)\\
Chappidi Lalith Aditya Reddy (1MS23CI145)\\
\end{flushright}


\thispagestyle{plain}
